Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-11 longoutput.tex
Fix typo
Add TODO for encrypting circuit
Fix bug
Start probability analysis

\section{Long Output scheme}

@@

@@

We then follow \cite{mahadev_delegation}. That is, the server would commit copies of the ground state of the Hamiltonian for the classical client to measure.

And then, this in fact involves some probabilistic analysis shenanigans that we haven't fully figured out yet.

>>>>

\section{Our Long Output Scheme}

@@

TODO Maybe encrypt things here first if needed?

@@

We then follow \cite{mahadev_delegation}. That is, the server would commit copies of the ground state of the Hamiltonian for the classical client to measure.
The client would keep a single copy for output, and use the other copies to check whether the computation is done properly.

Take $p_0$ and $p_1$ to be the probability to measure $\sgn(d_S)\braket{\phi|S|\phi}=-1$ on $\ket\psi$ and $\ket\phi$ respectively, where $\phi$ is perpendicular to $\psi$. Obviously, $p_0=\frac{1}{2}$, and $p_1<\frac{1}{2}$... TODO Now what? Hypothesis testing...?
